Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-20 article_review/Manuscript.tex
changes

When dealing with complex numerical models, analytical expressions of Sobol' indices are often inaccessible. In such cases, one must rely on an estimation of these indices. The original estimation procedure is due to Sobol' \cite{Sobol'}. However, this procedure requires several model evaluations which are usually expensive. Later on, Saltelli \cite{Saltelli} proposed strategies to estimate sets of Sobol' indices at once through the use of a combinatorial formalisms. While elegant, these strategies still require a large number of model evaluations.  A cost efficient alternative to estimate first-order indices was introduced in \cite{Mara}. This alternative, called the replication procedure, has recently been further studied  in \cite{Tissot} and generalized to the estimation of closed second-order indices.

@@

The uncertainty on $\vx$ is modeled by a uniform random vector, namely $\vx \sim \mathcal{U}(\cube)$. The Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$ is:
\begin{equation}
f(\vx)=f_{\varnothing}+\sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} f_u(\vx),
\label{anova}
\end{equation}
where:
\begin{align*}
f_{\varnothing} &= \mathbb{E}[f(\vx)]= \mu, \\
f_u(\vx) &= \int_{[0,1]^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subsetneq u} f_v(\vx).
\end{align*}
Due to orthogonality, the variance of equation \eqref{anova} leads to the variance decomposition of $f$:
\[ \sigma^2 = \mathrm{Var}[f(\vx)] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1]^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
From this decomposition, one can define the following two quantities:
\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad
\ov{$\tau$}_u^2 = \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2, \qquad u \subseteq \mathcal{D}.\]

@@

\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method (MC). The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
\centering
\vspace*{0.2cm}
\includegraphics[width=0.4\textwidth]{comp_MC_first.eps}
\label{compa_MC_first}
\end{figure}

\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\overline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method (MC). The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
\centering
\vspace*{0.2cm}
\includegraphics[width=0.4\textwidth]{comp_MC_tot.eps}
\label{compa_MC_tot}
\end{figure}}

>>>>

When dealing with complex numerical models, analytical expressions of Sobol' indices are often inaccessible. In such cases, one must rely on an estimation of these indices. The original estimation procedure is due to Sobol' \cite{Sobol'}. However, this procedure requires several model evaluations which are usually expensive. Later on, Saltelli \cite{Saltelli} proposed strat\-egies to estimate sets of Sobol' indices at once through the use of a combinatorial formalisms. While elegant, these strat\-egies still require a large number of model evaluations.  A cost efficient alternative to estimate first-order indices was introduced in \cite{Mara}. This alternative, called the replication procedure, has recently been further studied  in \cite{Tissot} and generalized to the estimation of closed second-order indices.

@@

The uncertainty on $\vx$ is modeled by a uniform random vector, namely $\vx \sim \mathcal{U}(\cube)$. The Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$ is:
\begin{equation}
f(\vx)=f_{\varnothing}+\sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} f_u(\vx),
\label{anova}
\end{equation}
where:
\begin{align*}
f_{\varnothing} &= \mathbb{E}[f(\vx)]= \mu, \\
f_u(\vx) &= \int_{[0,1]^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subsetneq u} f_v(\vx).
\end{align*}
Due to orthogonality, the variance of equation \eqref{anova} leads to the variance decomposition of $f$:
\[ \sigma^2 = \mathrm{Var}[f(\vx)] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2,\]
\[ \sigma_u^2=\int_{[0,1]^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
From this decomposition, one can define the following two quantities:
\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad
\ov{$\tau$}_u^2 = \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2, \qquad u \subseteq \mathcal{D}.\]

@@

\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method. The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
\centering
\vspace*{0.2cm}
\includegraphics[width=0.4\textwidth]{comp_MC_first.eps}
\label{compa_MC_first}
\end{figure}

\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\overline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method. The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
\centering
\vspace*{0.2cm}
\includegraphics[width=0.4\textwidth]{comp_MC_tot.eps}
\label{compa_MC_tot}
\end{figure}}
